Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-08-21 papers/cvpr2019/supplemental/skeleton-generation.tex
papers: added supplemental for cvpr2019

The second step is to run the actual skeletonization algorithm

@@

We created a skeleton benchmark to evaluate three different skeletonization approaches with varying downsampling parameters.

>>>>

The second step is to run the skeletonization algorithm.
We test three different algorithms.
As a baseline we use the built in \texttt{scipy:skeletonize\_3d} function that implements the medial surface/axis thinning algorithm of Lee et al.~\cite{lee1994building}.
This thinning algorithm preserves the topology and uses various post-processing techniques to reduce noise.
Second, we implement the TEASER skeletonization algorithm from Sato et al.~\cite{sato2000teasar}. 
This algorithm does not preserve topology but has shown promising results on various biomedical segmentations and variants of the strategy have been used on connectomics label volumes before~\cite{konstantin2018efficient,zhao2014automatic}.
Lastly, we implement, with the help of the author, a sequential curve-thinning algorithm based on isthmuses~\cite{palagyi2014sequential}.
This fast algorithm preserves topology and uses efficient lookup tables to reduce unnecessary computation.

@@

We created a skeleton benchmark to evaluate the three different skeletonization approaches with varying downsampling parameters.
We identify all of the endpoint locations
